Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-02 paper/main.tex
65% too long
little cleaning

% open question
In this study, we investigate if increased hemodynamic activity in the PPA that
is usually revealed by contrasting blocks of pictures can also be revealed by
contrasting selected stimulus features that incidentally occur under more
ecologically conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both visual and
auditory spatial information using two naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews).
% AV stimulus
The operationalization of visual perception is based on an annotation of cuts
and depicted locations in the audio-visual movie ``Forrest Gump'' (AV stimulus).
% AO stimulus
The operationalization of auditory perception is based on an annotation of
speech occurring in the movie's audio-description (AD stimulus).
% GLM contrasts
Based on these annotations, we created several general linear model (GLM)
contrast to analyze the corresponding publicly available fMRI datasets
(\href{http://www.studyforrest.org}{studyforrest.org}) of each naturalistic
stimulus \citep{hanke2016simultaneous, hanke2014audiomovie}.
% varying amount of data
Contrasts vary in HOW WELL / HOW MUCH DATA.\todo{intro too long already}

@@

We hypothesize[d] that an exclusively auditory stimulus can/could localize
``visual area'' in individual subjects and thus possibly substitute a
block-design experiment using pictures.
% hypo b
Further, we hypothesize[d] that an exclusively auditory stimulus can/could
localize the PPA in individual subjects, and thus substitute a visual experiment
be which would be more practicable to assess brain functions in visually
impaired persons.
% results: group
On a group average level,
% operationalization in naturalistic stimuli
results demonstrate that our approach based on annotations [of two ecologically
more valid stimuli] to operationalize spatial perception lead to increased
hemodynamic activity in [roughly] the same brain regions the block-designed
visual localizer.\todo{give an interpretation?}
% anterior vs. posterior
On both a group and individual subject level, a comparison of results from the
three datasets also suggests functional differences between the anterior and
posterior PPA.
% what does it mean
The current data add evidence to the hypothesis that the PPA might consist of
submodules that work together during visual perception of landscapes (cf.
\citep{baldassano2013differential}).
%
Lastly, our results suggest that the PPA's anterior part can be localized in
individual subjects by contrasting high-level semantic information occurring in
an auditory naturalistic stimulus.

@@

\begin{figure*}[h!]
\centering
    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
        correlation coefficients of the regressors used in the analysis of the
        audio-description (blue; see Table \ref{tab:ao-events} for a
        description) and audio-visual movie (red; see Table \ref{tab:av-events})
        rounded to the nearest tenth.
        The correlation between the two stimuli's
        root mean square loudness and between their left-right difference in
        loudness yielded the highest correlation values
        (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).
        \todo[inline]{not all labels are actually listed in that table}
      }
\label{fig:reg-corr}
\end{figure*}

@@

% similar to previous studies
On the first level, we created GLM contrasts like studies that contrasted blocks
of pictures.
% dissimilar
But unlike previous studies, our approach was to contrast selected stimulus
features that we annotated in the audio-visual movie and its audio-description.
% intro
To test the robustness of this approach, we operationalized the perception of
spatial information compared to the perception of ``non-spatial'' information
differently in five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}) and eight $t$-contrasts for the AD stimulus (see Table
\ref{tab:ao-contrasts})
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA.
% but we expect differences because
Nevertheless, we also assumed contrasts would differ in [?] \todo{differ in
what?  ``localization performance'' isn't well phrased. How ``well'', ``nice''
the results are?} since the event categories differed a) in how well the
averaged events reflected spatial information, and b) in available data (i.e.
event counts).
% difference to Sengupta; Berman et al. (2010). Evaluating functional localizers
(2010) Notably, localization of the PPA in individual subjects that was done by
\citep{sengupta2016extension} using the established approach of contrasting
blocks of pictures is based on one contrast for each subjects (cf. Table 3 in
\citep{sengupta2016extension}) that was chosen post-hoc from a set of three
contrasts (\textit{strict}, \textit{relaxed}, and \textit{simple} contrast
\citep{sengupta2016extension}).\todo{maybe add note regarding Berman (2010); but
they did FFA}
% thus: primary contrasts
Here, we chose one contrast to be ``primary contrast'' for later detailed
inspection and report.
% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well categories on average were assumed
to match the preferred stimulus type, and b) the amount of available data /

@@

\todo[inline]{nouns indicating switch to setting  and cuts to other setting are
"somewhat" correlated; cf. results -> discussion, part "random shower thoughts"}

@@

\section{Results}

\todo[inline]{SE: VIS wird selbst gar nicht/en passant berichtet, wäre aber
wichtig zum Andocken an Literatur}

@@

\todo[inline]{individual results: AD trifft besser die VIS-PPA "trifft" als AV.
    Das ist zumindest sehr überraschend, oder?; COH: actually it isn't because
    of blindly averaging the actual frame content in the categories of movie
    cuts (cf. methods/regressors, discussion/shortcomings)}

\todo[inline]{Bland-Altman-Plots: Welche Areale habt ihr als masks
genommen, FFA ist ja kartiert (Julia Caspers)}

% study goal
The goal of this study was to investigate if annotated hints about the spatial
layout embedded in two naturalistic stimuli correlate with increased hemodynamic
activity in the PPA.
% group level
On a group average level, we compare results gained from whole-brain GLM
analyses of the movie and the audio-description (Z>3.4; p<.05, cluster
corrected) to results gained from a traditional visual localizer
\citep{sengupta2016extension}.
% individual level
On the level single subjects (Z>3.4; p<.05, cluster corrected), we also assess
the performance of the exclusively auditory naturalistic stimulus as a
substitute for a visual paradigm to "localize" [?] the PPA.
% NeuroVault
Unthresholded $z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts co-registered to the group-template (MNI152 space) can found at
\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.  \todo{private
collection}

@@

% AV intro
First, we analyzed data from the movie offering a visual but ecologically more
valid stimulation than static pictures.
% AV primary contrast
The movie's primary $t$-contrast that compared cuts to a setting that was not
depicted before to cuts to a recurring setting (\texttt{vse\_new > vpe\_old})
yielded three significant clusters (see Table \ref{tab:res-av-group1}, Figure
\ref{fig:group-slices}).
% PPA (others the clusters extend into).
One cluster spans across the midline and comprises parts of the intracalcarine
and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
temporal fusiform gyrus and the parahippocampal cortex (reported from posterior
to anterior) in both hemispheres.
% LOC
Two additional homologous clusters are located in the superior lateral occipital
cortex (left bigger than right).

% AD intro
Second, we analyzed data from the audio-description offering exclusively
auditory stimulation.
% AD primary contrast
The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
non-spatial noun categories) yielded six significant clusters (see Table
\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
% overlap with ROI
Two homologous clusters are located in the anterior part of the PPA group
overlap that we gained from the visual localizer experiment.
% in detail
Specifically, these clusters are located at the borders of the posterior
parahippocampal cortex, the occipital and temporal fusiform gyrus and lingual
gyrus.\todo{Havard-Oxford atlas gives 3 different most prob. locations depen.
on voxel}
% precuneus
Two additional clusters are apparent in the ventral precuneus extending into the
retrosplenial cortex.
% LOC
Finally, two homologous clusters are located in the superior lateral occipital
cortex.

@@

% intro
Third, we investigated result from both naturalistic paradigms on the level of
individual subjects to ensure that the group results are not just a by-product
of the averaging process.
% AD is the real shit
Focussing on the AD stimulus, we hypothesize[d] that an exclusively auditory
stimulus can/could localize the PPA in individual subjects and thus
possibly substitute a visual paradigm [using blocks of pictures].

\todo[inline]{if we report procedure of Sengupta as detailed as it is now in the
following paragraph (imo it's too long), we probably need to explain the
differences between strict, relaxed, simple set in more detail in the method
section}
% Sengupta et al., 2016
The visual localizer experiment \citep{sengupta2016extension} yielded bilateral
[parahippocampal] clusters in 12 of 14 subjects and an unilateral right clusters
in two subjects (sub-04, sub-20).
% Sengupta: 1 of 3
Individual PPAs were assessed by visually inspecting thresholded $z$-maps
(Z>1.64, p<.05 cluster corrected) of three different $t$-contrasts
(\textit{strict}, \textit{relaxed}, and \textit{simple} stimulus set, cf.
\citep{sengupta2016extension}).
% procedure a)
Starting with the most conservative contrast (\textit{strict} set) and a
threshold of t = 2.5, we looked for clusters with at least 20 voxels (using
AFNI).
% procedure b)
We titrated [?] the threshold in the range of [2, 3] until we found an isolated
cluster for the PPA.
% Sengupta: procedure b)
If a cluster was not found or not isolated, we used a contrast from the
\textit{relaxed} set, or finally the \textit{simple} \todo{not used in any VP
for PPA}set, and repeated the process until we found a cluster that matched the
expected anatomical location based on literature \citep{epstein1998ppa}.

@@

% Discussion: explains how results fill gap identified in intro

@@

@@

\todo[inline]{the mother of total confusion: Aminoff shifts the PPA along the
    anterior-poster axis depending on publication;
    in Aminoff (2007, 2013):
    anterior PPA = spatial associations,
    region anterior to (!) PPA = non-spatial associations;
    in Aminoff (2015):
    posterior PPA = spatial associations,
    anterior PPA = non-spatial associations;
    hence: complete bullshit;
    ignore Aminoff (2015) due to various reasons}

>>>>

% open question
In this study, we investigate if increased hemodynamic activity in the PPA that
is usually revealed by contrasting blocks of pictures can also be revealed by
contrasting selected stimulus features that incidentally occur under more
ecologically conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both visual and
auditory spatial information using two naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews).
% AV stimulus
The operationalization of visual perception is based on an annotation of cuts
and depicted locations in the audio-visual movie ``Forrest Gump'' (AV stimulus).
% AO stimulus
The operationalization of auditory perception is based on an annotation of
speech occurring in the movie's audio-description (AD stimulus).
% GLM contrasts
Based on these annotations, we created several general linear model (GLM)
contrast to analyze the corresponding publicly available fMRI datasets
(\href{http://www.studyforrest.org}{studyforrest.org}) of each naturalistic
stimulus \citep{hanke2016simultaneous, hanke2014audiomovie}.

@@

We hypothesize[d] that an exclusively auditory stimulus can/could localize
``visual area'' in individual subjects and thus possibly substitute a
block-design experiment using pictures.
% hypo b
Further, we hypothesize[d] that an exclusively auditory stimulus can/could
localize the PPA in individual subjects, and thus substitute a visual experiment
be which would be more practicable to assess brain functions in visually
impaired persons.
% results: group
On a group average level,
% operationalization in naturalistic stimuli
results demonstrate that our approach based on annotations [of two ecologically
more valid stimuli] to operationalize spatial perception lead to increased
hemodynamic activity in [roughly] the same brain regions the block-designed
visual localizer.
% anterior vs. posterior
On both a group and individual subject level, a comparison of results from the
three datasets also suggests functional differences between the anterior and
posterior PPA.
% what does it mean
The current data add evidence to the hypothesis that the PPA might consist of
submodules that work together during visual perception of landscapes (cf.
\citep{baldassano2013differential}).
%
Lastly, our results suggest that the PPA's anterior part can be localized in
individual subjects by contrasting high-level semantic information occurring in
an auditory naturalistic stimulus.

@@

\begin{figure*}[h!]
\centering
    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
        correlation coefficients of the regressors used in the analysis of the
        audio-description (blue; see Table \ref{tab:ao-events} for a
        description) and audio-visual movie (red; see Table \ref{tab:av-events})
        rounded to the nearest tenth.
        The correlation between the two stimuli's
        root mean square loudness and between their left-right difference in
        loudness yielded the highest correlation values
        (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).
        \todo[inline]{not all labels are actually listed in that table; which
        ones are not listed? checked it, all labels listed}
      }
\label{fig:reg-corr}
\end{figure*}

@@

% similar to previous studies
On the first level, we created GLM contrasts like studies that contrasted blocks
of pictures.
% dissimilar
But unlike previous studies, our approach was to contrast selected stimulus
features that we annotated in the audio-visual movie and its audio-description.
% intro
To test the robustness of this approach, we operationalized the perception of
spatial information compared to the perception of ``non-spatial'' information
differently in five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}) and eight $t$-contrasts for the AD stimulus (see Table
\ref{tab:ao-contrasts})
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA.
% but we expect differences because
Nevertheless, we also assumed contrasts would differ in [?] \todo{differ in
what?  ``localization performance'' isn't well phrased. How ``well'', ``nice''
the results are?} since the event categories differed a) in how well the
averaged events reflected spatial information, and b) in available data (i.e.
event counts).
% difference to Sengupta; Berman et al. (2010). Evaluating functional localizers
(2010) Notably, localization of the PPA in individual subjects that was done by
\citep{sengupta2016extension} using the established approach of contrasting
blocks of pictures is based on one contrast for each subjects (cf. Table 3 in
\citep{sengupta2016extension}) that was chosen post-hoc from a set of three
contrasts (\textit{strict}, \textit{relaxed}, and \textit{simple} contrast
\citep{sengupta2016extension}).
% thus: primary contrasts
Here, we chose one contrast to be ``primary contrast'' for later detailed
inspection and report.
% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well categories on average were assumed
to match the preferred stimulus type, and b) the amount of available data /

@@

@@

\section{Results}
\todo[inline]{1400 words}

@@

% study goal
We investigated if spatial information embedded in two naturalistic stimuli
correlate with increased hemodynamic activity in the PPA.
% group level
On a group average level, we compare results gained from whole-brain GLM
analyses of the movie and the audio-description (Z>3.4; p<.05, cluster
corrected) to results gained from a traditional visual localizer
\citep{sengupta2016extension}.
% individual level
On the level single subjects (Z>3.4; p<.05, cluster corrected), we also assess
the performance of the exclusively auditory naturalistic stimulus as a
substitute for a visual paradigm to localize the PPA.
% NeuroVault
Unthresholded $z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts co-registered to the group-template (MNI152
space) can found at
\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.

@@

% AV intro
First, we analyzed data from the movie offering a visual but ecologically more
valid stimulation than static pictures.
% AV primary contrast
The movie's primary $t$-contrast that compared cuts to a setting that was not
depicted before to cuts to a recurring setting (\texttt{vse\_new > vpe\_old})
yielded three significant clusters (see Table \ref{tab:res-av-group1}, Figure
\ref{fig:group-slices}).
% PPA (others the clusters extend into).
One cluster spans across the midline and comprises parts of the intracalcarine
and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
temporal fusiform gyrus, and the parahippocampal cortex (reported from posterior
to anterior) in both hemispheres.
% LOC
Two additional homologous clusters are located in the superior lateral occipital
cortex.

% AD intro
Second, we analyzed data from the audio-description offering exclusively
auditory stimulation.
% AD primary contrast
The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
non-spatial noun categories) yielded six significant clusters (see Table
\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
% overlap with ROI
Two homologous clusters are located in the anterior part of the PPA group
overlap..
% in detail
Specifically, these clusters are located at the borders of the posterior
parahippocampal cortex, the occipital and temporal fusiform gyrus and lingual
gyrus.\todo{Havard-Oxford atlas gives 3 different most prob. locations depen.
on voxel}
% precuneus
Two additional clusters are apparent in the ventral precuneus extending into the
retrosplenial cortex.
% LOC
Finally, two homologous clusters are located in the superior lateral occipital
cortex.

@@

% intro
Third, we investigated result from both naturalistic paradigms on the level of
individual subjects to ensure that the group results are not just a by-product
of the averaging process.
% AD is the real shit
Furtherm, we hypothesized that an exclusively auditory
stimulus could localize the PPA in individual subjects and thus
possibly substitute a classic visual localizer experiment.

\todo[inline]{part regarding Sengupta is shortened; they used $t$-maps???}
% Sengupta et al., 2016
The visual localizer experiment \citep{sengupta2016extension} yielded bilateral
[parahippocampal] clusters in 12 of 14 subjects and an unilateral right clusters
in two subjects (sub-04, sub-20).
% Sengupta: 1 of 3
Individual PPAs were assessed by titrating [?] the $t$-threshold in the range
of [2, 3] in the thresholded $t$-maps (Z>1.64, p<.05 cluster corrected) of three
different $t$-contrasts (\textit{strict}, \textit{relaxed}, and \textit{simple}
stimulus set cf.  \citep{sengupta2016extension}) until we found an isolated
cluster that matched the expected anatomical location based on literature
\citep{epstein1998ppa}.

@@

\todo[inline]{2500 chars}
% Discussion: explains how results fill gap identified in intro

@@

\begin{comment}
    the mother of total confusion: Aminoff shifts the PPA along the
    anterior-poster axis depending on publication;
    in Aminoff (2007, 2013):
    anterior PPA = spatial associations,
    region anterior to (!) PPA = non-spatial associations;
    in Aminoff (2015):
    posterior PPA = spatial associations,
    anterior PPA = non-spatial associations;
    hence: complete bullshit;
    ignore Aminoff (2015) due to various reasons
\end{comment}

@@
